### 2023-12-13 main.tex
''

	\item \textit{\underline{Stirring generator}}: {\color{blue}this is the edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section \ref{sec1} (with $y=x+1$). As already pointed out, in this nearest neighbour chain, its action consists in exchanging the particles or the holes and the particles of two adjacent sites. Here we show that its action on the occupation variable of any species gives a discrete gradient in the occupation variable itself. Indeed, we have that }

>>>>

	\item \textit{\underline{Stirring generator}}: {\color{blue}this is the edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section \ref{sec1} (with $y=x+1$). As already pointed out, in this nearest neighbour chain, its action consists in exchanging two particles or an hole and a particle on two adjacent sites. Here we show that its action on the occupation variable of any species gives a discrete gradient in the occupation variable itself. Indeed, we have that }
